Pteropod biomarker analysis

### 2018-03-06 biomark.Rmd
added fluor to biomark and physio

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

@@

  levs1 <- quantile(md()$model[, 2],  c(0.25, 0.75)) %>% 
    list
  names(levs1) <- names(md()$model)[2]
  return(levs1)

@@

  levs2 <- quantile(md()$model[, 3], c(0.25, 0.75)) %>% 
    list
  names(levs2) <- names(md()$model)[3]
  return(levs2)

>>>>

envchr <- c('pCO2', 'pH', 'CO3', 'Ara', 'O2', 'Temp', 'Fluor')
ptechr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

@@

  levs1 <- quantile(md()$model[, 2],  c(0, 1)) %>% 
    list
  names(levs1) <- names(md()$model)[2]
  return(levs1)

@@

  levs2 <- quantile(md()$model[, 3], c(0, 1)) %>% 
    list
  names(levs2) <- names(md()$model)[3]
  return(levs2)
